Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-10-06 paper/paper.tex
Better here
A note
Experiment with a different style of plotting

\begin{figure}[tb]
    \centering\includegraphics{gen-graph-non-induced.pdf}
    \caption{Behaviour of algorithms on the non-induced variant. For each plot, the x-axis is the
        pattern edge probability and the y-axis is the target edge probability, both from 0 to 1.
        Along the top row, we show the proportion of instances which are satisfiable; the white
        bands shows the phase transitions, and the black lines are our predictions of where the
        phase transition will occur. On the final three rows, we show the number of search nodes used by the
        Glasgow, LAD and VF2 solvers; the dark regions indicate ``really hard'' instances.}
    \label{figure:non-induced}
\end{figure}

@@

@@

\section{Spuriously Hard Instances Outwith Graph Databases}

>>>>

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}
        \matrix {
            \node [anchor=center] {}; &
            \node [anchor=center] {\scriptsize $G(10, x){\rightarrowtail}G(150, y)$}; &
            \node [anchor=center] {\scriptsize $G(20, x){\rightarrowtail}G(150, y)$}; &
            \node [anchor=center] {\scriptsize $G(30, x){\rightarrowtail}G(150, y)$}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Satisfiable?}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-satisfiable-10.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-satisfiable-20.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-satisfiable-30.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Glasgow}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-nodes-10.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-nodes-20.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-nodes-30.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize LAD}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-non-induced-nodes-10.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-non-induced-nodes-20.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-non-induced-nodes-30.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize VF2}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-non-induced-nodes-10.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-non-induced-nodes-20.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-non-induced-nodes-30.pdf}}; \\
        };
    \end{tikzpicture}

    \caption{Behaviour of algorithms on the non-induced variant. For each plot, the x-axis is the
        pattern edge probability and the y-axis is the target edge probability, both from 0 to 1.
        Along the top row, we show the proportion of instances which are satisfiable; the white
        bands shows the phase transitions, and the black lines are our predictions of where the
        phase transition will occur. On the final three rows, we show the number of search nodes used by the
        Glasgow, LAD and VF2 solvers; the dark regions indicate ``really hard'' instances.}
    \label{figure:non-induced}
\end{figure}

@@

\subsection{Spuriously Hard Instances?}

?? However, by far the biggest problem is in graph databases. Not just lead to overly pessimistic
conclusions, but has misdirected the design of systems. Note that these deal with sparse, non-random
graphs.

@@
